|

### 2023-05-31 manuscript/Chapter2-appendix3.Rmd
update appendix S3

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences between the parameter values of each predator experience level predicted by the MDHGLM along with their and 95% HPD intervals. The test is displayed on the y axis (i.e. whether the experience level of interest has a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience levels being compared. The results are from the model that includes the outlier."}

@@

```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences in the correlations of players when they were advanced vs novice along with their 95% HPD intervals. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis. Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices. The results are from the MDHGLM that includes the outlier."}

>>>>

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% HPD intervals comparing the parameter values predicted by the MDHGLM among each predator experience level. The test is displayed on the y axis (i.e. whether the experience level of interest has a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience levels being compared. The results are from the model that includes the outlier."}

@@

```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and 95% HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels. The difference is displayed on the y axis and the correlated parameters are displayed on the x axis. Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices. The results are from the MDHGLM that includes the outlier."}
